---
title: "FIST Cards Report"
author: "Sofija Kostic"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{FIST Cards Report}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Project aim

The goal of `fistcards` is to create an online version of the FIST card task for
young children. The task uses cards that vary on three dimensions: colour,
animal, and number. The package currently provides helper functions for
representing the card deck, generating valid trials, scoring choices, and
running a small Shiny app.

This report is a draft for Week 3. The software is still being developed, so
later versions can add screenshots of the final app, more detail about the task
procedure, and examples from pilot data.

## Card structure

Each card is described by its colour, animal, number, and image path. The full
deck has 27 cards: three colours, three animals, and three numbers.

```{r}
library(fistcards)

cards <- fist_cards()
nrow(cards)
head(cards)
```

## Phase 1

In Phase 1, children see one target card and two possible answer cards. The
correct answer is the card that shares exactly one dimension with the target
card. The distractor shares no dimensions with the target. The two answer
options are also kept visually distinct from each other, so they do not share
colour, animal, or number.

```{r}
phase1_trials <- generate_phase1_trials(n = 5, seed = 1)
phase1_trials
```

The scoring helper returns the position of the correct choice.

```{r}
target <- list(colour = "blue", animal = "frog", number = 1)
choice1 <- list(colour = "yellow", animal = "frog", number = 3)
choice2 <- list(colour = "red", animal = "snail", number = 2)

correct_phase1_choice(choice1, choice2, target)
```

## Phase 2

In Phase 2, children see three cards and choose the special card. A valid
special card shares exactly one dimension with one card and exactly one
different dimension with the other card. The two non-special cards do not share
any dimensions with each other.

```{r}
phase2_trials <- generate_phase2_trials(n = 5, seed = 1)
phase2_trials
```

The scoring helper returns which of the three cards is the special card.

```{r}
card1 <- list(colour = "red", animal = "frog", number = 1)
card2 <- list(colour = "blue", animal = "frog", number = 2)
card3 <- list(colour = "red", animal = "snail", number = 3)

correct_phase2_choice(card1, card2, card3)
```

## Shiny app

The interactive version can be launched from R:

```{r, eval = FALSE}
devtools::load_all("fistcards")
run_fist_game()
```

The app currently includes:

- a participant ID field
- configurable trial counts for Phase 1 and Phase 2
- introductory example screens before each phase
- clickable card choices
- response recording with accuracy and reaction time
- CSV download at the end

## Testing and continuous integration

The package uses `testthat` unit tests for the card logic, trial generators, and
image assets. The Week 3 branch also adds a GitHub Actions workflow that should
run R CMD check on every push and pull request.

Locally, the tests can be run with:

```{r, eval = FALSE}
devtools::test("fistcards")
```

## Next steps

Planned next steps are to polish the child-facing wording, add final screenshots
to this report, and verify the workflow after opening the Week 3 pull request.
